\begin{thebibliography}{10}
\bibitem{ILOG} \emph{\url{https://www.ibm.com/it-it/products/ilog-cplex-optimization-studio}}
\bibitem{FICO} \emph{\url{https://www.fico.com/en/products/fico-xpress-optimization}}
\bibitem{GUROBI} \emph{\url{https://www.gurobi.com}}
\bibitem{CBC} \emph{\url{https://www.coin-or.org/Cbc/}}
\bibitem{concorde} \emph{\url{http://www.math.uwaterloo.ca/tsp/concorde/index.html}}
\bibitem{monnalisa} \emph{\url{http://www.math.uwaterloo.ca/tsp/data/ml/monalisa.html}}
\bibitem{COMPACT_CITE} A. Orman, H. Williams, A Survey of Different Integer Programming Formulations of the Travelling Salesman Problem, In: \emph{Optimisation, Econometric and Financial Analysis}, vol. 9, pp. 96-98, Springer, 2007.
\bibitem{VNS_CITE} P. Hansen, N. Mladenovic, J. Brimberg, J. A. Moreno Pèrez, M. Gendreau, J. Potvin, Variable Neighborhood Search, In: \emph{Handbook of Metaheuristics}, International Series in Operations Research \& Management Science, vol.57, pp. 61-86, Springer, 2010.
\bibitem{SA} L. Fang, P. Chen, S. Liu, Particle Swarm Optimization with Simulated Annealing for TSP, In: \emph {Proceedings of the 6th Conference on 6th WSEAS Int. Conf. on Artificial Intelligence, Knowledge Engineering and Data Bases}, vol.6, pp. 206-210, 2007.
\bibitem{TSP} M. Fischetti, In: \emph {Lezioni di Ricerca Operativa}, Cap.8, pp. 183-185, Kindle Direct Publishing, 2018.
\bibitem{local_branching} M. Fischetti, A. Lodi, Local branching, In: \emph {Mathematical Programming}, Ser. B, vol.98, pp. 23-47, Springer-Verlag, 2003.
\bibitem{hybrid_VNS} S. Hore, A. Chatterjee, A. Dewanji, Improving variable neighborhood search to solve the traveling salesman problem, In: \emph {Applied Soft Computing}, vol.98, pp. 83-91, Elsevier, 2018.
\end{thebibliography}